Dynamic Transition Analysis with TIMES

### 2018-01-12 doc/poster.tex
the poster size was wrong.
Former-commit-id: 1d2d535ae3206e8f27a81032157657208435e7f1

\usepackage[scale=1.0]{beamerposter} % Use the beamerposter package for laying out the poster
\usetheme{confposter} % Use the confposter theme supplied with this template

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\paperheight}{48in} % A0 height: 33.1in
\setlength{\textwidth}{34in} % A0 width: 46.8in
\setlength{\textheight}{46in} % A0 height: 33.1in
\setlength{\sepwid}{0.025\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.3\paperwidth} % Width of one column
\setlength{\twocolwid}{0.625\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.95\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

\author{\textbf{Energy Analysis Division}\\
        \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy 
        Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

Evaluate potential impact of novel energy technologies within Japan's energy system. Specifically:
\begin{itemize}
	\item Guide practical near term (2010-2050) transition strategies.
        \item Minimize carbon emissions within realistic constraints.
	\item Identify high impact technologies.
	\item Assess role of technology readiness.
	\item Predict impediments to strategically optimal technology deployment.
	\item Identify ideal timelines for energy system deployment, infrastructure development, high impact R\&D investment.
\end{itemize}

@@

\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.  
\end{block}

@@

%----------------------------------------------------------------------------------------
%	Anticipated Results
%----------------------------------------------------------------------------------------

\begin{block}{Anticipated Results}

 \begin{itemize}
   \item Analysis results can be filtered by sector (commercial, industrial, residential, building etc) or by region.

   \item Many metrics are automatically postprocessed- such as energy intensity, thermal energy efficiency, transmission capacity.

   \item Technology deployment transitions driven by constrained optimization will have valuable strategic value.

 \end{itemize}

@@

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

        \begin{alertblock}{Impact}
        \large Results will:
	\begin{itemize}
        \item {Optimize realistic decarbonization roadmaps.}
        \item {Identify potential transition bottlenecks.}
        \item {Help Japan's policymakers create timelines for R\&D investment and infrastructure development.}
        \item {Quantify system sensitivity to technology readiness.}
	\end{itemize}
        \end{alertblock}

@@

@@

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Summary}
\begin{itemize}

\item Dynamic simulation of Japan's energy system transition in the TIMES model 
        generator will help develop near-term decarbonization strategies.
\item Policymakers will benefit from identification of high impact technologies, and creation of R\&D investment and infrastructure development timelines.
\item Simulations will quantify system sensitivity to technology readiness.

\end{itemize}

>>>>

\usepackage[scale=0.9]{beamerposter} % Use the beamerposter package for laying out the poster
\usetheme{confposter} % Use the confposter theme supplied with this template

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{33.1in} % A0 width: 46.8in
\setlength{\paperheight}{46.8in} % A0 height: 33.1in
\setlength{\textwidth}{33.1in} % A0 width: 46.8in
\setlength{\textheight}{46.8in} % A0 height: 33.1in
\setlength{\sepwid}{0.025\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.3\paperwidth} % Width of one column
\setlength{\twocolwid}{0.625\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.95\paperwidth} % Width of three columns
\setlength{\topmargin}{-1in} % Reduce the top margin size
%-----------------------------------------------------------

@@

\author{
       % \textbf{ENERGY ANALYSIS DIVISION}\\
       % \textbf{I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions}\\
        Anshuman Chaube, James Stubbins, \textbf{Kathryn Huff}}
\institute{University of Illinios at Urbana-Champaign, Department of Nuclear, Plasma, and Radiological Engineering, Urbana, IL 61801}
%----------------------------------------------------------------------------------------

@@

\begin{description}
{\large 
        \item[\textbf{Division:}] Energy Analysis Division
        \item[\textbf{Project:}] I\textsuperscript{2}CNER Initiative on Challenges in Energy Assessment and Energy Transitions
        \item[\textbf{Objective:}] Evaluate potential impact of novel energy technologies within Japan's energy system.
\item[\textbf{Milestones:}] ~\\}
        \begin{itemize}
        \item Minimize carbon emissions within realistic constraints.
        \item Optimize realistic 2010-2050 decarbonization roadmaps.
	\item Identify high impact technologies.
        \item Identify potential transition bottlenecks.
        \item Help Japan's policymakers create timelines for R\&D investment and infrastructure development.
        \item Quantify system sensitivity to technology readiness.
	\item Predict impediments to strategically optimal technology deployment.
	\end{itemize}
\end{description}

@@

@@

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function (such as minimizing carbon emissions or costs) is solved within user defined constraints such as energy generation demand.

\begin{description}
        \item[\textbf{Sector Analysis:}] TIMES models can resolve generation and 
                 consumption by sector (commercial, industrial, residential, 
                 building etc). 
         \item[\textbf{Regional Analysis:}] TIMES can also resolve regions.
         \item[\textbf{Post-Processing:}] Many metrics are automatically postprocessed 
                 (i.e. energy intensity, thermal energy efficiency, 
                 transmission capacity).. 
         \item[\textbf{Constrained Optimization}] Modeling technology deployment 
                 transition as a constrained optimization problem will
                 drive insights.
 \end{description}

@@

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------

        \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Dynamic simulation of Japan's energy system transition in 
                        the TIMES model generator will help develop near-term 
                        decarbonization strategies.
                \item Policymakers will benefit from identification of high 
                        impact technologies, and creation of R\&D investment 
                        and infrastructure development timelines.  
                \item Simulations will quantify system sensitivity to 
                        technology readiness. 
                \item Dynamic analysis will identify potential transition 
                        bottlenecks.
	\end{itemize}
        \end{alertblock}

@@
